 \subsubsection{INFN Trieste} 
 \label{sec:infn-planned-next}
For 2019, we confirm the planning that was presented in
June 2018 including two activities.
\begin{enumerate}
\item
\textbf{Single photon detector 
by MPGD technologies with 
miniaturized 
pad-size}. \\
The analysis of the data collected at the 2018 
test beam exercise where a first version of the 
prototype will be completed.\\
The realization and characterization by laboratory 
tests of a
second version of the prototype is also foreseen. 
The construction of this second version of the
prototype is 
related to the observed non-uniformity of the gain. 
As explained in the June 2018 report
the source of the effect has been understood:
it is related to the design of the anode PCB 
of the MM multiplication
stage. A modified version has already been designed. 
The construction and characterization 
of the modified prototype
will take place in 2019.
\item
\textbf{Innovative photocathode 
based on NanoDiamond (ND) particles} \\
The initial studies to understand the 
compatibility of a photocathode 
based on NanoDiamond (ND) particles with the 
operation in gaseous detectors and, in 
particular, in MPGD-based photon detectors, 
have been performed in 2018. The characterization of
THGEMs with ND 
coating, both in the case of hydrogenated and
non-hydrogenated powder has presented unexpected
features, even if 
very different in the two cases.
The 2019 activity will be dedicated to further 
explore these 
performance in order to understand the origin of the
modified
THGEM behavior by producing under 
controlled parameters       a new set 
of small-size THGEMs, 
that then will be fully characterized.
\end{enumerate}
\par
Following the activity planning, the 
\textbf{milestones for 2019} are:
\begin{itemize}
\item
September 2019: The completion of the laboratory characterization 
of the second version of the photon detector with miniaturized pad-size.
\item
September 2019: The completion of the studies to understand the performance of THGEMs with ND coating, both in the hydrogenized and non-hydrogenized versions.
\end{itemize}